The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-08-30 tex/MNRAS_submission/rv1/referees_reply.txt

	We thank the Referee for reading our manuscript carefully and for their review and comments.
	We address each of these in turn below (indented text).

	We have also made further, key improvements to our dataset and pipeline.

	We note that after the submission of the original manuscript it was brought to our attention
	(K. Perger; priv. comm) that we were missing a handful of confirmed z>5 quasars.
	As such, our database has increased by 25 objects for a total of 488 VHzQs.

	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA Science Archive (VSA) from scratch
	with the set of updated objects. This uncovered a small matching bug for three objects in the WSA
        (no issues were found in the VSA rerun). One of these objects, however, is SDSSJ2220-0101, which
	we thought had large photometric changes but now acknowledge this was due to an incorrect
	apertureID measurement. The updated photometry for SDSSJ2220-0101 has the VSA J-band
	magnitude 19.38+/-0.04 and a WSA magnitude 19.24+/-0.09.

	Consequently, we have changed the Abstract:
	"Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had
	significant differences between their WFCAM and VISTA
	magnitudes in one band."
	to
	"Only one quasar, SDSS J0349+0034, shows significant
	differences between WFCAM and VISTA magnitudes in one band."

### 2019-09-09 tex/VHzQ.tex
tables_for_paper/LIST_OF_VHzQs.dat updated
Added Appendix detailing changes to Qso input catalogue

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the 
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

\subsection{Spectroscopy} 
We compile the list of all known, spectroscopically confirmed
quasars from the literature.  This list was complied from a range of
surveys and papers.  Specifically, we use data from:
\citet{Banados2014, Banados2016, Banados2018a, Banados2018b}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{Douglas2007}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
\citet{Kashikawa2015}, 
\citet{Khorunzhev2017}, 
\citet{Koptelova2017}, 
\citet{Kozlowski2019}, 
\citet{Kim2015, Kim2018},  
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Saxena2018}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{vanBreugel1999}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018a, YangJ2018b}  
and 
\citet{Zeimann2011}.

@@

We thank:
\begin{list}{$\circ$}{}  
  \item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
  \item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
  \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
  \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
  \item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
  \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
\end{list}

@@

@@

%\bibliographystyle{apj}
%\bibliographystyle{mn2e}
\bibliographystyle{mnras}
\bibliography{/cos_pc19a_npr/programs/quasars/highest_z/tex/tester_mnras}

>>>>

We have compiled a list of {\bf 488} quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the 
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

\subsection{Spectroscopy} 
We compile the list of all known, spectroscopically confirmed
quasars from the literature.  This list was complied from a range of
surveys and papers.  Specifically, we use data from:
\citet{Banados2014, Banados2016, Banados2018a, Banados2018b}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{Douglas2007}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
\citet{Kashikawa2015}, 
\citet{Khorunzhev2017}, 
\citet{Koptelova2017}, 
\citet{Kozlowski2019}, 
\citet{Kim2015, Kim2018},  
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Saxena2018}, 
\citet{Schneider2007}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{vanBreugel1999}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018a, YangJ2018b}  
and 
\citet{Zeimann2011}.

{\bf We updated our list of objects between the submitted paper and accepted due
to feedback from other scientists. We discuss these changes in detail in
Appendix~\ref{app:qso_sample}.}

@@

We thank:
\begin{list}{$\circ$}{}  
  \item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
  \item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
  \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
  \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
  \item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
  \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
  \item Krisztina Perger at \href{http://astro.elte.hu} for discussions about
  the input catalogue. 
\end{list}

@@

\section{Qso Sample}
\label{app:qso_sample}
{\bf In the submitted version of this paper, we had 463 QSOs selected from the
literature which had $z\geq5$, which we thought was the complete sample except a
few that were published in 2019.

When we posted the submitted paper onto arXiv\footnote{http://www.arxiv.org}, we
had two responses, one from Jinyi Yang, who pointed out that we missed QSOs in
\cite{YangJ2018a} and Krisztina Perger, who also mentioned that we had
missed $sim40$ QSOs and pointed us to her catalogue of
QSOs\footnote{http://astro.elte.hu/~perger/catalog.html}. We downloaded Tables
2,3 \& 4 from \cite{YangJ2018a} using
Vizier\footnote{http://vizier.u-strasbg.fr/} and found all matches with 
$2\arcsec$ and added the remaining objects that had $z\geq5$, one object  from
Table 3, SUHAWJ1016+2541, and 15 from Table 4, see Table~\ref{tab:new_qsos}. We
also downloaded the 20190514 version of the Perger catalogue and X-matched that,
finding all of the matches with $2\arcsec$ and looked for non-matches.

However, we spotted some inconsistences between the names of some of the QSOs
in the Perger catalogue and decimal equatorial coordinates and pointed these
out, and very rapidly Perger responded having fixed their catalogue. After
further checks we found 10 objects (see Table~\ref{tab:disagree_objs}) that were
in both catalogues that there was disagreement on the coordinates. In some cases it
was clear from the names that either we (Ross \& Cross) had made a typo, or
Perger had. In most other cases a search of the literature gave a clear answer. 
Two particular odd examples were SDSSJ0835+3227 and VA-13492, found in the
Perger catalogue. In both cases the coordinates looked similar to SDSSJ0835+3217 
and SDSSJ1040-1155 respectively and the redshifts were identical to these QSOs,
which alerted us to a potential problem. These QSOs could be traced back in the literature: in
the first case both QSOs are in \cite{Banados2016} and in the second case is 
VA-13492  is in \cite{Flesch2015} which refers back to \cite{Douglas2007}
although the latter only seems to only contain SDSSJ1040-1155.
In the case of SDSSJ0835+3227, we checked the SDSS-z band images\footnote{https://dr15.sdss.org}, and found a bright source at
the position of SDSSJ0835+3217 and no source at the position of SDSSJ0835+3227, see
Figure~\ref{fig:check_obj}. In the case of VA-13492, the I-band magnitude was
equivalent to SDSSJ1040-1155 (I=25.9 mag), so we have decided that both of these objects
have been transcribed incorrectly sometime in the past.

The objects from the submitted version of Ross \& Cross that have changed
position are flagged in Table~\ref{tab:disagree_objs} and the difference in position is
shown. Some of these are rounding errors using coordinates that were to the
nearest arcsec or $4\arcsec$ if it was rounded to the nearest hour, minute,
second in RA, some were typos from reentering coordinates and these demonstrate
that it is always better to download electronic catalogues and use decimal coordinates.
Perger has also updated their catalogue and the 20190724 version matches our
catalogue. A final test of matching to with $1\arcsec$ found another difference:
we had downloaded the OGLEJ015531-75 coordinates from the published paper and
Perger had done so from the submitted arXiv paper, and it seems that
\cite{Kozlowski2019} made a minor update to their values in between.

We also excluded DES0141-54, that was included in the Perger catalogue, since
this came from a conference proceedings \cite{Belladitta2018}, which did not
have arcsecond precision in its coordinates, so our matched-aperture photometry
may have been in an incorrect position.

Altogether we found that our final catalogue has 488 $z\geq$ QSOs. The new QSOs
are all shown in Table~\ref{tab:new_qsos}.}

%% Table New QSOs --> name, ra, dec, redshift, reference, source
%% Table QSOs in disagreement --> name, correct pos, difference, literature,
% ErrorInCR, TypeOfError

\begin{table*}   
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & redshift & reference & source  \\
\hline  
SUHAWJ1016+2541 & +154.1571250 & +25.6921944 & +5.64 &Yang2018 & Yang2018 \\
PS1J0052+4556 & +13.1810417	& +45.9422306 & +5.31 & Yang2018   & Yang2018 \\
PS1J0332+1811 & +53.1540833	& +18.1998000 & +5.12 & Yang2018   & Yang2018 \\
PS1J0511-0754 & +77.9780417	& -7.9123056 & +5.13 & Yang2018 & Yang2018 \\
PS1J0616-1338 & +94.1015833	& -13.6351111	& +5.58 & Yang2018 & Yang2018 \\
PS1J0757-0002 & +119.4412500 & -0.0336361 & +5.54 &	Yang2018 & Yang2018 \\
PS1J0817-1633 & +124.2527500 & -16.5581361 & +5.06 & Yang2018 & Yang2018 \\
PS1J1034-1233 & +158.6535833 & -12.5618028 & +5.51 & Yang2018 & Yang2018 \\
PS1J1057-1758 & +164.3650000 & -17.9754722 & +5.34 & Yang2018 & Yang2018 \\
PS1J1121-0718 & +170.4318750 & -7.3110250 & +5.71 & Yang2018 & Yang2018 \\
PS1J1137-1049 & +174.3973750 & -10.8262611 & +5.50 & Yang2018 & Yang2018 \\
PS1J1310-0639 & +197.5546250 & -6.6643222 & +5.06 & Yang2018  & Yang2018 \\
PS1J1313-2617 & +198.3585833 &-26.2893972 & +5.54 & Yang2018 & Yang2018 \\
PS1J1427-0503 & +216.8398333 & -5.0647333 & +5.08 & Yang2018 & Yang2018 \\
PS1J1533-1810 & +233.4990000 &-18.1742250 & +5.03 & Yang2018 & Yang2018 \\
PS1J2033+1218 & +308.2936250 & +12.3143028 & +5.11 & Yang2018 & Yang2018 \\
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & +5.09 & Kozlowski2019 & Perger
\\
TNJ0924-2201 & +141.0830000	& -22.0281940 & +5.19 & vanBreugel1999 & Perger \\
XMMJ125329+30 & +193.3725460 & +30.9276197 & +5.08 & Khorunzhev2017 & Perger \\
SDSSJ141912.03+53 & +214.8001310 &+53.6775646 & +5.38 & Paris2017 & Perger \\
TGSSJ1530+1049 & +232.7079167 & +10.8253060	& +5.72 & Saxena2018 & Perger \\
PSOJ352.4034-15.337 & +352.4034850 & -15.3373500 & +5.84 & Banados2018 & Perger
\\
PSOJ0046-2837 & +11.5985420	& -28.6298170 & +5.99 & Venemans2018 & Perger \\
VIKJ2318-3029 & +349.6379420 & -30.4926030 & +6.1458 & Venemans2018 & Perger \\
HSC1732+6531 & +263.1796583	& +65.5204139 & +6.60 & Songaila2018 & Other \\
\hline  \hline
\end{tabular}
\caption{{\bf New QSOs added to the paper since the submitted version. }
}
\label{tab:new_qsos}
\end{table*}

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & difference & isCRDiff & Issue \\
 & deg & deg & arcsec & &  \\
\hline
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
%% Same name diff pos/redshift from v1
PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
%%Krisztina wrong\ldots
SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
%% More complex 
SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
VA-13492 & --- & --- & --- & No & 6 \\
\hline  
\hline  \hline
\end{tabular}
\caption{{\bf QSOs in disagreement between RC and Perger or which have been
updated since the submitted paper.
This table shows all of the QSOs where there has been a disagreement or a
change. All of those marked 'Yes' were in the submitted paper and have been
changed since, and the final column lists the reason(s) for inclusion in the
table. The numbers refer to the following issues:
\begin{itemize}
	\item 1) Coordinate update in original reference, from submitted to accepted; 
	\item 2) Coordinate different in RC submitted
	\item 3) Redshift different in RC submitted, typically very small changes. 
	\item 4) Our coords incorrect, but KP had 2 entries, one also incorrect
	\item 5) Coordinates incorrect in KP.
	\item 6) Two objects with similar looking coordinates and identical redshifts.
	These appear to be incorrect entries further back in the literature. 
\end{itemize}  
}}
\label{tab:disagree_objs}
\end{table*}

\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083525+3217.jpg}
  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083526+3227.jpg}
  \centering
  %\vspace{-12pt} 
  \caption[]
  {{\bf Cutouts from SDSS z-band images retrieved from SDSS-SkyServer for the
  coordinates of SDSSJ083535+3217 and SDSSJ083526+3227. Both of these objects
  appear in \cite{Banados2016} and subsequently in the Perger catalogue, but
  only SDSSJ083535+3217 is matched to an SDSS source. Since SDSSJ083526+3227
  has an SDSS name, and is apparently a $z=5.89$ QSO, it should have a z-band
  detection.}}
  \label{fig:check_obj}
\end{figure}

@@

%\bibliographystyle{apj}
%\bibliographystyle{mn2e}
\bibliographystyle{mnras}
\bibliography{./tester_mnras}
